---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

One practice Wilson et al. suggests is good software practice. Specifically making code that is "readable, reusable, and testable." The best way to implement this in R is by having very clear variable names throughout the code and having comments before blocks of coding explaining what the code is doing in words. In addition, explaining, in words, the inputs and outputs of the script also help make code readable. It is also good to keep code chunks small and not repetitive. Functions are a good way to make code understandable and looping through a list is better than having a large number of closely related variables. 

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4)**13
```

4) Push this homework to the GitHub repository for the homework. 





